\section{Course program}
The course is structured into six lectures.
The six lectures take place during the six weeks of the course, but are not necessarily in a one-to-one correspondence with the course weeks. For example, lectures one and two are fairly short and can take place during a single week.

\subsection{Chapter 1 - Intro to design patterns}
\paragraph*{Topics}
\begin{itemize}
	\item What are design patterns?
	\item Visiting polymorphic instances.
	\item Pure object-oriented Visitor pattern
	\item Functional approach to Visitor pattern
\end{itemize}

\subsection{Chapter 2 - Iterating collections}
\paragraph*{Topics}			
\begin{itemize}
	\item What is an iterator?
	\item Why using iterators?
	\item Iterating a generic collection.
\end{itemize}


\subsection{Chapter 3 - Entity construction and event management}
\paragraph*{Topics}			
\begin{itemize}
	\item Creating object without specifying the class type.
	\item Subscribing, observing, and notifying events.
\end{itemize}



\subsection{Chapter 4 - Building state machines}
\paragraph*{Topics}			
\begin{itemize}
	\item Selecting the program behaviour at runtime.
	\item Strategy pattern
	\item State machines over strategy pattern.
\end{itemize}

\subsection{Chapter 5 - Extending behaviours}
\paragraph*{Topics}			
\begin{itemize}
	\item Specializing behaviours of entities.
	\item Decorator pattern.
\end{itemize}

\subsection{Chapter 6 - Composing behaviours}
\paragraph*{Topics}			
\begin{itemize}
	\item Managing different objects with shared behaviours.
	\item Adapter pattern.
\end{itemize}
