\section{Assessment}
The course is tested with two exams:
A series of \glspl{assignment} which have to be handed in, but won't be graded. There will be an \gls{oral}, which is based on the \glspl{assignment}
and a written exam. The final grade is determined as follows: \\

\texttt{if \gls{exam}-grade $ >= 5.5 $ then return \gls{oral}-grade else return 0}

\paragraph*{Motivation for grade}
A professional software developer is required to be able to program code which is, at the very least, \textit{correct}.

In order to produce correct code, we expect students to show:
\begin{inparaenum}[\itshape i\upshape)]
\item a foundation of knowledge about how a programming language actually works in connection with a simplified concrete model of a computer;
\item fluency when actually writing the code.
\end{inparaenum}

The quality of the programmer is ultimately determined by his actual code-writing skills, therefore the written exam will require you to write code; this ensures that each student is able to show that his work is his own and that he has adequate understanding of its mechanisms.


\subsection{Theoretical examination \modulecode}
The general shape of a \gls{exam} for \texttt{\modulecode} is made up of a short series of highly structured open questions.
In each exam the content of the questions will change, but the structure of the questions will remain the same.
For the structure (and an example) of the theoretical exam, see the appendix.


\subsection{Practical examination \modulecode}
There is one \glspl{assignment} that is mandatory.

The assignment asks you to implement a GUI system in the fashion of Windows Form with an immediate drawing library, such as Monogame. In the assignment you have to show that you can use effectively some of the design patterns learnt during the course. Your GUI library should allow to create at least clickable buttons and text labels organized in a single panel. Optionally you can implement a system with a scrollable panel. You are free to choose the implementation details as long as you show the usage of design patterns. Each design pattern that it is correctly use will increase the grade of the assignment (see below for further details).

\begin{itemize}
  \item All assignments are to be presented at the end of the oral assessment to the teacher upon request
  \item Each assignment is designed to assess the students knowledge related to one or more \glspl{lo}.
          If the teacher is unable to assess the students' ability related to the appropriate \gls{lo} based on his work, then no points will be awarded for that part.
  \item At the oral check you will be given 1 point for each design pattern learnt in class which is used \textit{appropriately} in your assignment to a maximum of 4 points. At the oral check you will be asked to solve one ore more exercises on design patterns. The maximum score for this part is up to 6 points. The final grade for the oral check will be the sum of the points for the assignment and the one for the exercises.
  \begin{itemize}
  	\item The design patterns used for the assignment should be those seen in the course: visitor, decorator, abstract, iterator, and adapter.
  	\item Factories can be used to abstract away the creation of elements of the form.
  	\item Decorators can be used to extend the behaviors of GUI controls
  	\item Etc..  	
  \end{itemize}
  \item \textit{The teachers still reserve the right to check the practicums handed in by each student, and to use it for further evaluation.}
  \item The university rules on fraude and plagiarism (Hogeschoolgids art. 11.10 -- 11.12) also apply to code;
\end{itemize}
