\section{Course program}
The course is structured into six lectures.
The six lectures take place during the course, but are not necessarily in a one-to-one correspondence with the course weeks.

\subsection{Chapter 0 - reuse through generics}
\paragraph*{Topics}			
\begin{itemize}
	\item Using generic parameters
	\item (\textbf{Advanced}) Using covariance and contravariance in the presence of generic parameters
	\item (\textbf{Advanced}) Designing interfaces and implementation in the presence of generic parameters
\end{itemize}

\subsection{Chapter 1 - Intro to design patterns} 
\paragraph*{Topics}
\begin{itemize}
	\item What are design patterns? \glssymbol{undbeh}
	\item Visiting polymorphic instances. \glssymbol{impbeh}
	\item Pure object-oriented Visitor pattern \glssymbol{impbeh}
	\item Functional approach to Visitor pattern \glssymbol{impbeh}
\end{itemize}

\subsection{Chapter 2 - Iterating collections}
\paragraph*{Topics}			
\begin{itemize}
	\item What is an iterator? \glssymbol{undbeh}
	\item Why using iterators? \glssymbol{undbeh}
	\item Iterating a generic collection. \glssymbol{impbeh}
\end{itemize}

\subsection{Chapter 3 - Extending behaviours}
\paragraph*{Topics}			
\begin{itemize}
	\item Decorator pattern. \glssymbol{undstr}
	\item Decorating over iterator. \glssymbol{impstr}
\end{itemize}


\subsection{Chapter 4 - Entity construction}
\paragraph*{Topics}			
\begin{itemize}
	\item Creating object without specifying the class type. \glssymbol{undcre}, \glssymbol{impcre}
\end{itemize}


\subsection{Chapter 5 - Adapting behaviours}
\paragraph*{Topics}			
\begin{itemize}
	\item Managing different objects with shared behaviours. \glssymbol{undstr}
	\item Adapter pattern. \glssymbol{impstr}
\end{itemize}